Resolvable Ambiguity

### 2019-07-08 paper/paper.tex
Consistent syntax pass through section 6

\begin{description}
\item[$\dfa(l)$:] Given the production $N -> l : r$, compute the regular language $L' := L(r) \setminus \{N'_m \mid N' \in \NT, m \subseteq \Labels\}$. Then replace every marked non-terminal $N'_m$ with the regular expression $l_{1l_1 \in m} + l_{2l_2 \in m} + \ldots + l_{nl_n \in m}$, where $l_i$ are all the labels of productions $N' -> l_i : r_i$, e.g., $E_{\{a\}}$ in the running example would be replaced by $l_\bot + a_\top + m_\bot + n_\bot$. Then construct a DFA for this language.

@@

We have implemented a tool and a small DSL for syntax definition
that generates a language definition in the style of
Section~\ref{sec:parse-time-disambiguation}, which the tool then
uses to construct a parser and do a dynamic resolvability
analysis. The tool is implemented in Haskell and uses an
off-the-shelf
implementation\footnote{\url{http://hackage.haskell.org/package/Earley}}
of the Earley parsing algorithm
\cite{earleyEfficientContextfreeParsing1970}. The purpose of these
case studies is to showcase possible use cases of resolvable
ambiguity in the context of a pre-existing general purpose
programming language (OCaml, Section~\ref{sec:evaluation-ocaml}),
a pre-existing DSL (Orc, Section~\ref{sec:evaluation-orc}), and a
new DSL (Cyphym, Section~\ref{sec:evaluation-cyphym}).

>>>>

\begin{description}
\item[$\dfa(l)$:] Given the production $N -> l : r$, compute the regular language $L' := L(r) \setminus \{N'_m \mid N' \in \NT, m \subseteq \Labels\}$. Then replace every marked non-terminal $N'_m$ with the regular expression $l_1_{l_1 \in m} + l_2_{l_2 \in m} + \ldots + l_n_{l_n \in m}$, where $l_i$ are all the labels of productions $N' -> l_i : r_i$, e.g., $E_{\{a\}}$ in the running example would be replaced by $l_\bot + a_\top + m_\bot + n_\bot$. Then construct a DFA for this language.

@@

We have implemented a tool and a small DSL for syntax definition that generates a language definition in the style of Section~\ref{sec:parse-time-disambiguation}, which the tool then uses to construct a parser and do a dynamic resolvability analysis. The tool is implemented in Haskell and uses an off-the-shelf implementation\footnote{\url{http://hackage.haskell.org/package/Earley}} of the Earley parsing algorithm \cite{earleyEfficientContextfreeParsing1970}. The purpose of these case studies is to showcase possible use cases of resolvable ambiguity in the context of a pre-existing general purpose programming language (OCaml, Section~\ref{sec:evaluation-ocaml}), a pre-existing DSL (ORC, Section~\ref{sec:evaluation-orc}), and a new DSL (Cyphym, Section~\ref{sec:evaluation-cyphym}).
